High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-11-26 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source. The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au. Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprising thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with 
%VLT/SPHERE 
the current generation of high-contrast images 
has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}. The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}. The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars. A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}. The observations revealed diverse structures and morphologies in the scattering surface of these discs. This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} in a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.

@@

V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016. All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published. Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circum rather than inter-stellar material.

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights. The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required. Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization. The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
$\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$. For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.87$\pm$0.94\,au.

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$. There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA, could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}.).

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $\delta(r)$ parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

%The $\delta(r)$ function, that account for deviations from the power law, is defined as:
%\begin{align}
%\delta(r) = \left\{ \begin{array}{cc} 
%                 5E-6 & \hspace{5mm} 0.3<r<5 \\
%                 5E-3 & \hspace{5mm} 5<r<8  \\
%                 5E-5 & \hspace{5mm} 8<r<12\\
%                 2.5E-2 & \hspace{5mm} 12<r<19.5 \\
%                 1E-8 & \hspace{5mm} 19.5<r<20.5 \\
%                 1E-4 & \hspace{5mm} 20.5<r<25 \\
%                 1.7E-1 & \hspace{5mm} 25<r<120 \\
%                \end{array} \right.
%\end{align}

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indexes $\psi$. The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is $H_\circ = 0.045$ at $r_0 = 19.5$\,au.

@@

Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

The two different populations of dust grains corresponds to the small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.

>>>>

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA. ***
  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed current knowledge of planet formation. The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with 
%VLT/SPHERE 
the current generation of high-contrast images 
has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}. The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}. The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars. A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}. The observations revealed diverse structures and morphologies in the scattering surface of these discs. This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.

@@

V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016. All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published. Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights. The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required. Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits**). The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$. For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.*** %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, 
Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below). ***
%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 265\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$. There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA. This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.~\ref{fig:SED}). The SED will provide us with missing information about the dust population.

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indexes $\psi$. The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is $H_\circ = 1$\,au at $r_\circ = 19$\,au.

We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. Then it is defined by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disk follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.

We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=6$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=1\times10^{13}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.

For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
with $\delta_{\mathrm{sd}}$ = 5.2$\times 10^4$. But the inner wall of Ring24 follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 19.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.6\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the model large-grain density at 64\,au. The large-dust surface density profile is defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$. For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au. Thus, the surface density of the outer ring of large grains dust is defined by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large-dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}
